---
title: "From Frequentist Problems Towards Bayesian Solutions"
subtitle: "Part 1: Replication crisis in Psychology <br> (and what does Statistics have to do with it)"
author: "Jorge N. Tendeiro"
date: "10 August 2019"
output: 
  ioslides_presentation:
    smaller: true
    transition: slower
    logo: figures/rugr_logoenv_rood_rgb.png
    css: slides.css
bibliography: references.bib
csl: apa-old-doi-prefix.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

[comment]: # (See here: https://stackoverflow.com/questions/42690955/how-to-insert-footnotes-in-ioslides-presentations-using-rmarkdown/45569765)
<style>
div.footnotes {
  position: absolute;
  bottom: 0;
  margin-bottom: 10px;
  width: 80%;
  font-size: 0.6em;
}
</style>

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>
<script>
$(document).ready(function() {
  $('slide:not(.backdrop):not(.title-slide)').append('<div class=\"footnotes\">');

  $('footnote').each(function(index) {
    var text  = $(this).html();
    var fnNum = (index+1).toString();
    $(this).html(fnNum.sup());

    var footnote   = fnNum + '. ' + text + '<br/>';
    var oldContent = $(this).parents('slide').children('div.footnotes').html();
    var newContent = oldContent + footnote;
    $(this).parents('slide').children('div.footnotes').html(newContent);
  });
});
</script>






# Fraud

## Definition
Fraud = scientifc misconduct.

- Falsifying data.
- Fabricating data.
- 





# Questionable research practices

## QRPs
Coin termed by @john2012a.<br>
See also @simmons2011a.
<br><br>

- Not necessarily fraud.
- Includes the (ab)use of actually *acceptable* research practices.
- Problem with QRPs:<br>
    * Introduce bias (typically, in *favor* of the researcher's intentions...).
    * Inflate effect size.
    * Results not replicable.

## QRPs
Some examples [@john2012a; @schimmack2015]: 

- Omit some DVs.
- Omit some conditions.
- Uncontrolled sequential testing --- Look and decide:
    * $p > .05$: Collect more
    * $p < .05$: Stop.
- $p = .054 \longrightarrow p = .05$.
- Only report $p<.05$ results.
- Exclusion of outliers dependent on $p$.
- Convert exploratory result into research question.
- ...

# But *why*?...

## Why risking scientific misconduct?
It is strongly related to incentives [@nosek2012a; @schonbrodt2015].

- "Publish or perish":<br>
Publish a lot, at highly prestigious journals.
- Journals only publish a fraction of all manuscripts.
- 







## R Markdown
Some more text.<footnote>And *another* **footnote**</footnote>

$x^2 = \exp\left(\frac{\sqrt{a}}{b}\right)$

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1<footnote> *Humm* **errr**</footnote>
- Bullet 2
- Bullet 3

Enter one at a time:

> - aaa
> - bbb
> - ccc

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

### <b>
x <- 10
y <- x * 2
### </b>

## Slide with Plot

```{r pressure}
plot(pressure)
```

# References

----

<style>
slides > slide { overflow: scroll; }
slides > slide:not(.nobackground):after {
  content: '';
}
</style>

