---
title: "From Frequentist Problems Towards Bayesian Solutions"
author: "Jorge N. Tendeiro"
date: "10 August 2019"
output: 
  ioslides_presentation:
    smaller: true
    transition: slower
    logo: figures/rugr_logoenv_rood_rgb.png
    css: slides.css
    template: quarterly-report.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

[comment]: # (See here: https://stackoverflow.com/questions/42690955/how-to-insert-footnotes-in-ioslides-presentations-using-rmarkdown/45569765)
<style>
div.footnotes {
  position: absolute;
  bottom: 0;
  margin-bottom: 10px;
  width: 80%;
  font-size: 0.6em;
}
</style>

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>
<script>
$(document).ready(function() {
  $('slide:not(.backdrop):not(.title-slide)').append('<div class=\"footnotes\">');

  $('footnote').each(function(index) {
    var text  = $(this).html();
    var fnNum = (index+1).toString();
    $(this).html(fnNum.sup());

    var footnote   = fnNum + '. ' + text + '<br/>';
    var oldContent = $(this).parents('slide').children('div.footnotes').html();
    var newContent = oldContent + footnote;
    $(this).parents('slide').children('div.footnotes').html(newContent);
  });
});
</script>













# Section maybe? | Let's see\ldots

## R Markdown
Some more text.<footnote>And *another* **footnote**</footnote>

$x^2 = \exp\left(\frac{\sqrt{a}}{b}\right)$

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1<footnote> *Humm* **errr**</footnote>
- Bullet 2
- Bullet 3

Enter one at a time:

> - aaa
> - bbb
> - ccc

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

### <b>
x <- 10
y <- x * 2
### </b>

## Slide with Plot

```{r pressure}
plot(pressure)
```

